---
title: "Simple document Git Testing"
author: "Hongtong Lin"
date: "2026-09-17"
output: 
  github_document:
          toc: true
          toc_depth: 3
---

I'm an R Markdown document! 

# Section 0: libraries 
##### 'load libraries' is the name of this r chunk. naming each code chunks will help you check where the bugs are.  

##### 'message=F' in the R chunk intro means that all of the messy info will be hidden.  

##### 'eval=F' prevents the code inside a specific chunk from being executed when you knit the document.
```{r load_libraries,messgae =F, eval=T}
library(tidyverse)
library(ggplot2)
```

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3: a tibble 

```{r}
plot_df = tibble(
  x = rnorm(1000, sd = .5),
  y = 1 + 2 * x + rnorm(1000)
)
head(plot_df)
```

# Section 4: Plot 
##### 'echo=F' in the r chunk intro means the results will show up in the kinnted document
```{r, echo =F} 
ggplot(plot_df, aes(x = x)) + geom_histogram() #histogram

ggplot(plot_df, aes(x = x, y = y)) + geom_point() #scatterplot of x and y
```

# Section 5: learning assignment 2  

Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about echo = FALSE?  

This plot shows the distribution of the absolute value of $X \sim N(1,1)$. **(this is the latex language)**

```{r learning assignment 2}
set.seed(1)
# Fixes the random number generator's starting point. Without it, rnorm() draws
# a different 500 numbers every time you knit, so your histogram and any numbers

la_df <- tibble(
  x = rnorm(500, mean = 1), # rnorm() = draw from a normal distribution. Smaple size of 500, mean =1, sd=1 by defult
  pos = x>0,
  abs_x = abs(x)
)

ggplot(
  la_df,
  aes(x = abs_x)
) + geom_histogram()

```

The median is `r round(median(la_df$x),2)`. The code is `round(median(la_df$x),2) or round(median(pull((la_df, x)),2)`

# Section 6: Text formatting
Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell

# Section 7: Learning assignment 3  

After the previous code chunk, write a bullet list given the mean, median, and standard deviation of the original random sample.  

* the medain is `r round(median(la_df$x),2)`.  
* the mean is `r round(mean(la_df$x),2)`.  
* the standard deviation is `r round(sd(la_df$x),2)`.
